\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_09.tex
Major change

\section{Rate of convergence via the doubling variables method}
\noindent The main result is the following Theorem.
\begin{thm}\label{thm:rate_doubling1} Let $\Omega$ be an open, bounded and connected subset $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and $1<p<2$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
\end{equation*}
\end{thm}

@@

Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2}, we define the auxiliary functional

@@

    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta,

@@

where $C_0$ is the Lipschitz constant of $u^0$ (also the Lipschitz constant of $u_\delta$ for $\delta>0$). We split the proof into several steps.

@@

\color{blue}
\item[2.] Assume that $x_\sigma\notin \overline{\Omega}_\delta$, i.e., $d(x_\sigma) < \delta$. Let $\underline{x}_\sigma\in \partial\Omega_\delta$ be the projection of $x_\sigma$ onto $\partial\Omega_\delta$, then $d(\underline{x}_\sigma) = \delta$ and for all $z\in \partial\Omega$ then

@@

    |\underline{x}_\sigma - x_\sigma| \leq C\delta. \qquad (\color{red} C<1) \color{blue}

@@

Now $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,\underline{x}_\sigma)$ gives us that
    \begin{align}\label{e:est_sigma2-new}
        \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} &\leq \frac{C_0|x_\sigma-\underline{x}_\sigma|^2}{\sigma} +  u_\delta(\underline{x}_\sigma) - u_\delta(y_\sigma)  \nonumber \\
        &\leq  \frac{C_0|x_\sigma-\underline{x}_\sigma|^2}{\sigma} + C_0|\underline{x}_{\sigma} - y_\sigma|.
    Therefore
        |x_\sigma - y_\sigma|^2 &\leq \sigma|\underline{x}_\sigma - y_\sigma| + |x_\sigma - \underline{x}_{\sigma}|^2 \\
        &\leq \sigma|\underline{x}_\sigma - x_\sigma| + \sigma|x_\sigma - y_\sigma| + |x_\sigma - \underline{x}_\sigma|^2\\
        &\leq \sigma|x_\sigma - y_\sigma| + \delta \sigma + \delta^2\leq \frac{|x_\sigma - y_\sigma|^2}{2} + 2\sigma^2 + \delta\sigma +\delta^2.
    Therefore

@@

        |x_\sigma - y_\sigma|^2 \leq 4\sigma^2 + 2\delta\sigma + 2\delta^2

@@

    Let $\delta = \theta \sigma$ for $\theta > 1$, then

@@

        |x_\sigma - y_\sigma|^2\leq 2\sigma^2(\theta+2)^2

@@

\color{black}
\item[2.] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that

@@

     \frac{C_0|x_\sigma-y_\sigma|^2}{\sigma} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.

>>>>

\section{Rate of convergence via the doubling variables method}
\noindent The main result is the following Theorem.
\begin{thm}\label{thm:rate_doubling1} Let $\Omega = B(0,1)$ be the open unit ball in $\mathbb{R}^n$. Assume $\mathrm{(A1)},\mathrm{(H1)}-\mathrm{(H4)}$ and also $1<p<2$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u^0$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
    0\leq u^\varepsilon(x) - u^0(x) \leq C\sqrt{\varepsilon} \qquad\text{for}\;x\in \Omega_{2\sqrt{\varepsilon}}.
\end{equation*}
\end{thm}

@@

Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimate
    \sup_{x\in \overline{\Omega}_\delta} \left(|u_\delta(x)| + |Du_\delta(x)|\right) \leq C_0.
We define the auxiliary functional

@@

    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y+\delta \nabla d(x)|^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.

@@

We split the proof into several steps.

@@

\item[2.] The unit outward normal vector at a point $z\in \partial\Omega$ is given by 

@@

    \mathbf{n}(z) = -\nabla d(z).

@@

The projection of $x_\sigma$ to $\partial\Omega$ is given by

@@

    \underline{x}_\sigma = x_\sigma + d(x_\sigma)\mathbf{n}(\underline{x}_\sigma).

@@

Assume $0<d(x_\sigma) < \delta$, then clearly 

@@

    x_\sigma - \delta \mathbf{n}(\underline{x}_\sigma) \in \overline{\Omega}_\delta.

@@

From $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma-\delta \mathbf{n}(\underline{x}_\sigma))$ we have

@@

     \frac{C_0|x_\sigma-y_\sigma - \delta\nabla d(x_\sigma)|^2}{2\sigma^2} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.

### 2021-04-06 Drafts and notes/Attempts/Old_draft_10.tex
Major change

\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
\begin{equation}\label{e:PDE_delta}
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
    \end{cases} \tag{PDE$_\delta$}
Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimate
    \sup_{x\in \overline{\Omega}_\delta} \left(|u_\delta(x)| + |Du_\delta(x)|\right) \leq C_0.
We define the auxiliary functional
    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|x-y+\delta \nabla d(x)|^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
We split the proof into several steps.
\begin{enumerate}
    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that 
    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
We can assume that 
\begin{equation}\label{e:ass_delta0}
    d(x_\sigma) < \delta_0
so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
\item[2.] The unit outward normal vector at a point $z\in \partial\Omega$ is given by 
    \mathbf{n}(z) = -\nabla d(z).
The projection of $x_\sigma$ to $\partial\Omega$ is given by
    \underline{x}_\sigma = x_\sigma + d(x_\sigma)\mathbf{n}(\underline{x}_\sigma).
Assume $0<d(x_\sigma) < \delta$, then clearly 
    x_\sigma - \delta \mathbf{n}(\underline{x}_\sigma) \in \overline{\Omega}_\delta.
From $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma-\delta \mathbf{n}(\underline{x}_\sigma))$ we have
    \begin{equation}\label{e:est_sigma2}
     \frac{C_0|x_\sigma-y_\sigma - \delta\nabla d(x_\sigma)|^2}{2\sigma^2} \leq u_\delta(x_\sigma) - u_\delta(y_\sigma) \leq C_0|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \sigma.
    This gives us that
    \begin{equation}\label{e:est_sigma3}
        d(x_\sigma) \geq d(y_\sigma) - |x_\sigma-y_\sigma|\geq \delta-\sigma.
    Let $\delta = 2\sigma$, we deduce that $d(x_\sigma)\geq \sigma$.
    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, thus by subsolution test for \eqref{eq:PDEeps} we have
\begin{align}\label{e:sub1}
    &\lambda u^\varepsilon(x_\sigma) + \left|\frac{2C_0(x_\sigma-y_\sigma)}{\sigma} - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|^p - f(x_\sigma)\nonumber\\
    &\qquad\qquad -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0.
\item[4.] Let
\begin{equation}\label{e:est_xi_zeta}
    \xi_\sigma = \frac{2C_0(x_\sigma-y_\sigma)}{\sigma} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma)
then $|\xi_\sigma|\leq 2C_0$ by \eqref{e:est_sigma2} and furthermore $\xi_\sigma+\zeta_\sigma \in D^-u^\varepsilon(x_\sigma)$, which, by the local gradient estimate, as $x_\sigma\in \Omega_{\sigma}$, $\xi_\sigma+\zeta_\sigma$ is bounded in terms of $\sigma$ and will blow up as $\sigma\to 0$. Nevertheless, we can do better as following.
    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right| \leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} 
    &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
    &= \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}
by choosing $\sigma = \varepsilon^\gamma$ where
 \displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}.
In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.

>>>>

\begin{proof}[Proof of Theorem \ref{thm:rate_doubling1}] Let $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ be the state-constraint solution to
\begin{equation}\label{e:PDE_delta}
    \begin{cases}  
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \leq 0 \qquad\text{in}\; \Omega_\delta\\
    \lambda u_\delta(x) + H(x,Du_\delta(x)) \geq 0 \qquad\text{on}\; \overline{\Omega}_\delta.
    \end{cases} \tag{PDE$_\delta$}
\end{equation} 
Let $C_f$ be the Lipschitz constant of $f$ and $\beta,\sigma,\delta \in (0,1)$ to be chosen later. Recall the definition of $C_\varepsilon$ from Theorem \ref{thm:wellposed1<p<2} and a priori estimate
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \left(|u_\delta(x)| + |Du_\delta(x)|\right) \leq C_0.
\end{equation*}
We define the auxiliary functional
\begin{align*}
    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{C_0|(1+\delta)x-y |^2}{2\sigma^2}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta.
\end{align*}
We split the proof into several steps.
\begin{enumerate}
    \item[1.] Since $u^\varepsilon (x)d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}_\delta$ such that 
\begin{equation*}
    \max_{\overline{\Omega}\times \overline{\Omega}_\delta} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
\end{equation*}
We can assume that 
\begin{equation}\label{e:ass_delta0}
    d(x_\sigma) < \delta_0
\end{equation}
so that $|Dd(x_\sigma)| = 1$. We will mention how the case $d(x_\sigma)\geq \delta_0$ is easily deduced at the end of the proof.
\item[2.] Since $x_\sigma\in \Omega = B(0,1)$, we have $(1-\delta)x_\sigma \in B(0,1-\delta) = \Omega_\delta$ and by convex combination, for any $\eta\in (0,1)$ we have
\begin{equation*}
    \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \in \overline{\Omega}_{\delta}.
\end{equation*}
by definition of the maximum of $\Phi^\sigma(x_\sigma,y_\sigma)$ we have
\begin{equation*}
    \Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma\Big(x_\sigma, \eta (1-\delta)x_\sigma + (1-\eta)y_\sigma \Big).
\end{equation*}
That is
\begin{align*}
    &- u_\delta(y_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma \big|^2}{2\sigma^2} \\
    &\qquad\qquad\geq  - u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - \frac{C_0\big|(1+\delta)x_\sigma - \eta (1-\delta)x_\sigma - (1-\eta)y_\sigma \big|^2}{2\sigma^2}.
\end{align*}
Therefore
\begin{align*}
    \frac{C_0}{2\sigma^2}\big|(1+\delta)x_\sigma - y_\sigma \big|^2 &\leq u_\delta\Big(\eta (1-\delta)x_\sigma + (1-\eta)y_\sigma\Big) - u_\delta(y_\sigma) \\
    &\qquad\qquad  + \frac{C_0}{2\sigma^2}\Big|\eta2\delta x_\sigma + (1-\eta)\big((1+\delta)x_\sigma-y_\sigma\big)\Big|^2
\end{align*}

\item[2.] Since $x_\sigma\in \Omega = B(0,1)$, we have $(1-\delta)x_\sigma \in B(0,1-\delta) = \Omega_\delta$, thus by definition of the maximum of $\Phi^\sigma(x_\sigma,y_\sigma)$ we have
\begin{equation*}
    \Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma, (1-\delta) x_\sigma).
\end{equation*}
That is
\begin{align*}
    &u^\varepsilon(x_\sigma) - u_\delta(y_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma \big|^2}{2\sigma^2} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}\\
    &\qquad\qquad\quad \geq  u^\varepsilon(x_\sigma) - u_\delta((1-\delta)x_\sigma) - \frac{C_0\big|(1+\delta)x_\sigma - (1-\delta)x_\sigma \big|^2}{2\sigma^2} - \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}.
\end{align*}
Therefore we obtain that
    \begin{equation}\label{e:est_sigma2}
     \frac{C_0|(1+\delta)x_\sigma-y_\sigma|^2}{2\sigma^2} \leq u_\delta((1-\delta)x_\sigma) - u_\delta(y_\sigma) + \frac{C_0|2\delta x_\sigma|^2}{2\sigma^2}. 
    \end{equation}
    Let $\delta = m \sigma^\kappa$, from \eqref{e:est_sigma2} we have
    \begin{equation}\label{e:est_sigma3n}
        \frac{C_0|(1+\delta)x_\sigma-y_\sigma|^2}{2\sigma^2}  \leq 2C_0(1+m^2).
    \end{equation}
    This gives us that
    \begin{equation}\label{e:est_snow}
      \big|(1+\delta)x_\sigma - y_\sigma\big|   \leq 2\sigma\sqrt{1+m^2\sigma^{2(\kappa-1)}},
    \end{equation}
    therefore
    \begin{equation}\label{e:e2}
     |x_\sigma| \leq \frac{1-\delta}{1+\delta} + \frac{2\sigma}{1+\delta}.
    \end{equation}
    As $\Omega = B(0,1)$, we have $d(x) = 1-|x|$ for $x\in \Omega$, therefore
    \begin{equation*}
        d(x_\sigma) = 1- |x_\sigma| \geq 1 - \left(\frac{1-\delta}{1+\delta} + \frac{2\sigma}{1+\delta}\right) = \frac{2(\delta - \sigma)}{1+\delta}.
    \end{equation*}
    Choose 
    \begin{equation}\label{e:scale_sigma}
        \sigma = \frac{\delta}{2}
    \end{equation}
    we deduce that
    \begin{equation}\label{e:snow_7}
    d(x_\sigma)\geq \frac{\delta}{1+\delta} \geq \frac{\delta}{2} = \sigma
    \end{equation}
    if we choose only $0<\delta < 1$.
    \item[3.] $x\mapsto \Phi^\sigma(x,y_\sigma)$ has a maximum at $x_\sigma\in \Omega$, i.e.,
    \begin{equation*}
        u^\varepsilon(x) - \left(\frac{C_0|(1+\delta)x-y_\sigma|^2}{2\sigma^2} + \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}\right)
    \end{equation*}
    has a maximum at $x_\sigma\in \Omega$. By subsolution test for \eqref{eq:PDEeps} we have
\begin{align}\label{e:sub1}
    &\lambda u^\varepsilon(x_\sigma) + \left|\xi_\sigma+\zeta_\sigma\right|^p - f(x_\sigma)\nonumber\\
    &\quad  -\varepsilon\left(\frac{2n}{\sigma} + \frac{C_\varepsilon(\alpha+\beta)(\alpha+\beta+1)|D d(x_\sigma)|^2}{d(x_\sigma)^{\alpha+\beta+2}}-\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}\Delta d(x_\sigma)\right)  \leq 0
\end{align}
where 
\begin{equation}\label{e:est_xi_zeta}
    \xi_\sigma = \frac{C_0\big((1+\delta)x_\sigma-y_\sigma\big)}{\sigma^2} \qquad\text{and}\qquad \zeta_\sigma = - \frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma).
\end{equation}
We have the following estimates
\begin{align*}
    |\zeta_\sigma|=\left|\frac{C_\varepsilon(\alpha+\beta)}{d(x_\sigma)^{\alpha+\beta+1}}D d(x_\sigma )\right|
    &\leq \frac{C_\varepsilon(\alpha+\beta)}{\sigma^{\alpha+\beta+1}} \\
    &\leq \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha} \frac{\varepsilon^{\alpha+1}}{\sigma^{\alpha+\beta+1}} \\
    &= \frac{(\alpha+\beta)(\alpha+1)^{\alpha+1}}{\alpha}\varepsilon^{\alpha+1 - \gamma(\alpha+1+\beta)}
\end{align*}
by choosing $\sigma = \varepsilon^\gamma$ where
\begin{equation*}
 \displaystyle 0 < \gamma < \frac{\alpha+1}{\alpha+1+\beta}.
\end{equation*}
In particular, $|\zeta_\sigma|\leq \mathfrak{C}_\alpha$ where $\mathfrak{C}_\alpha = \alpha^{-1}(\alpha+\beta)(\alpha+1)^{\alpha+1}$.

\noindent On the other hand, we need to improve the estimate \eqref{e:est_snow} to make sure that $|\xi_\sigma|$ is bounded. From \eqref{e:est_sigma2} we have
\begin{align*}
    \frac{C_0\big|(1+\delta)x_\sigma - y_\sigma\big|^2}{2\sigma^2} &\leq u_\delta((1-\delta)x_\sigma) - u_\delta(y_\sigma) \\
    &\leq C_0\big|(1-\delta)x_\sigma - y_\sigma\big| \leq C_0\Big(|(1+\delta)x_\sigma - y_\sigma| + 2\delta|x_\sigma|\Big)
\end{align*}
which implies that 
\begin{equation*}
    \big|(1+\delta)x_\sigma - y_\sigma\big|^2 \leq 2\sigma^2 \big|(1+\delta)x_\sigma - y_\sigma\big| + 4\delta \sigma^2 \leq 12\sigma^3 
\end{equation*}
since $|x_\sigma|\leq 1$ and \eqref{e:est_snow}. Therefore we have a new estimate for $|\xi_\sigma|$ as follows.
